Radio Emission from Red-Giant Hot Jupiters

### 2015-09-22 ms.tex
independent section for inoization fraction

Before estimating the frequency of planetary radio emission and its radio spectral intensity, we specify the property of the planetary magnetic field in \S\ref{ss:magneticfield}, and that of the stellar wind of the evolved stars in \S\ref{ss:stellarwind}.  
Then, we discuss the framework to estimate the frequency and intensity of planetary radio emission in \S\ref{ss:model_frequency} and \S\ref{ss:model_intensity}, respectively.

@@

@@

In reality, not all released electrons may be able to proceed the next ionization.
If $\xi$ represents the fraction of released electrons that proceed to the next ionization, then the number of ionized atoms $N_i$ released through this cascade (\emph{i}), is
%%%%%%%%%
\begin{eqnarray}
  \nonumber N_i & = & (1-\xi) + 2\xi (1-\xi) + 4 \xi^2 (1-\xi) + 8 \xi^3 \\
  \label{eq:N_i1} & = & 1 + \xi + 2 \xi^2 + 4 \xi ^3 \, .
\end{eqnarray}
%%%%%%%%%
With $\xi = 0.8 $, this gives $N_i \sim 5$.  \memoDS{Why 0.8?}
Alternatively, cascade (\emph{ii}) leads to
%%%%%%%%%
\begin{eqnarray}
  \nonumber N_i & = & \frac{1 - \xi^\nu}{1 - \xi} \\
  \label{eq:N_i2}  & = & 1 + \xi + \xi^2 + \cdots + \xi^{\nu - 1} \, ,
\end{eqnarray}
%%%%%%%%%
where $\nu \equiv E_{\rm in} / E_{\rm Rydberg}$ is the maximum number of ionizations for the given initial electron energy.
This limit leads to a value for $N_i$ that is not dramatically different from that of limit (\emph{ii}).
In Appendix \ref{sec:AppendixB}, we estimate the Bhabha(/M{\o}ller) scattering cross section and show that cascade (\emph{ii}) is probably more realistic.

>>>>

Before estimating the frequency of planetary radio emission and its radio spectral intensity, we specify some ingredients. 
The property of the planetary magnetic field is described in \S\ref{ss:magneticfield}, and the stellar wind of the evolved stars is discussed in \S\ref{ss:stellarwind}.  
In \S\ref{ss:ionization}, we consider the ionization around the planets because it is a crucial factor to determine the efficiency of the planetary magnetosphere and the stellar wind. 
Then, we proceed to the framework to estimate the frequency and intensity of planetary radio emission in \S\ref{ss:model_frequency} and \S\ref{ss:model_intensity}, respectively.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Ionization around the planet}
\label{ss:ionization}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

In reality, not all released electrons may be able to proceed the next ionization.
If $\xi$ represents the fraction of released electrons that proceed to the next ionization, then the number of ionized atoms $N_i$ released through this cascade (\emph{i}), is
%%%%%%%%%
\begin{eqnarray}
  \nonumber N_i & = & (1-\xi) + 2\xi (1-\xi) + 4 \xi^2 (1-\xi) + 8 \xi^3 \\
  \label{eq:N_i1} & = & 1 + \xi + 2 \xi^2 + 4 \xi ^3 \, .
\end{eqnarray}
%%%%%%%%%
%With $\xi = 0.8 $, this gives $N_i \sim 5$.  \memoDS{Why 0.8?}
Alternatively, cascade (\emph{ii}) leads to
%%%%%%%%%
\begin{eqnarray}
  \nonumber N_i & = & \frac{1 - \xi^\nu}{1 - \xi} \\
  \label{eq:N_i2}  & = & 1 + \xi + \xi^2 + \cdots + \xi^{\nu - 1} \, ,
\end{eqnarray}
%%%%%%%%%
where $\nu \equiv E_{\rm in} / E_{\rm Rydberg}$ is the maximum number of ionizations for the given initial electron energy.
This limit leads to a value for $N_i$ that is not dramatically different from that of limit (\emph{ii}).
In Appendix \ref{sec:AppendixB}, we estimate the Bhabha(/M{\o}ller) scattering cross section and show that cascade (\emph{ii}) is probably more realistic.
